### 2014-05-08 intro.tex
Add some learnability to intro

Once we had a computerized protocol designer, we explored using it as
a tool to gain understanding about the problem of congestion control.
How easy is it to ``learn'' a network protocol to achieve desired
goals, given a necessarily imperfect model of the networks where it
ultimately will be deployed? Is there a tradeoff between the
performance of an algorithm now---if optimized for a very specific
network---versus the protocol's ability to perform adequately as the
network evolves? What is the cost of compatibility with existing TCP
congestion-control mechanisms? Our experimentation into these
questions of ``learnability'' is reported in
Chapter~\ref{chap:learnability}.

>>>>

Once we had a computerized protocol designer, we explored using it as
a tool to gain understanding about the problem of congestion control.
How easy is it to ``learn'' a network protocol to achieve desired
goals, given a necessarily imperfect model of the networks where it
ultimately will be deployed? Is there a tradeoff between the
performance of an algorithm now---if optimized for a very specific
network---versus the protocol's ability to perform adequately as the
network evolves? What is the cost of compatibility with existing TCP
congestion-control mechanisms?

Our experimentats into these questions of ``learnability'' are reported
in Chapter~\ref{chap:learnability}. We found:

\begin{itemize}

\item Weak evidence of a tradeoff between the breadth of the operating
  range of a computer-generated protocol and its performance.

\item Modeling a two-bottleneck network as a single bottleneck hurt
  performance mildly.

\item Building in ``TCP-awareness'' to a computer-generated protocol
  helped in the case when cross-traffic was governed by TCP, but made
  the protocol more aggressive (and consequently increased delay) when
  it was contending only against other cross-traffic generated by the
  same algorithm.

\end{itemize}
